\documentclass[letterpaper]{article} % or whatever
\usepackage[margin=0.75in]{geometry}

\usepackage{titlesec}
\usepackage{supertabular}
\usepackage{hanging}

\usepackage{parskip}
\setlength{\parindent}{15pt}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}


\begin{document}

\pagestyle{empty}


%--------------------TITLE-------------
\par{\centering
		{\Huge\textsc{Sean Gref}
	}\bigskip\par}

\begin{center}
seangref@gmail.com $\bullet$ 479 62nd St Apt 1R, Brooklyn, NY 11220 $\bullet$ 951-287-8129
\end{center}

%\par\noindent\rule{\textwidth}{0.4pt}

% \textbf{Summary: } Passionate developer ready to create world-class products. Eager to integrate with the team and begin writing code. 

\section{Work Experience}
\vspace{0.5em}

\noindent\begin{large}\textsc{Meijun}\end{large} - San Diego\\
\indent Software Engineer \textit{8/2015 - Present}
\begin{itemize}
\item Architected, implemented, and released applications, websites, and mobile apps in a fast-paced environment with high standards of quality.
\item Produced software on time and below budget with very little supervision by independently defining tasks and creating timelines.
\item Interfaced directly with technical and non-technical clients to effectively communicate project updates and product support.
\item Experience working in a team and alone to produce responsive UIs, robust APIs, and scalable services for a diverse set of clients.
\end{itemize}

\section{Education}
\vspace{0.5em}
\noindent\begin{large}\textsc{University of California, San Diego}\end{large} \textit{8/2013 - 9/2017}
\\B.S. Computer Science and Engineering
\begin{itemize}
\item Courses include: Software Engineering \textit{(CSE 110)}, Computer Security \textit{(CSE 127)}, Compilers \textit{(CSE 135)}, Graphics Programming \textit{(CSE 167)}
\item Maintained cumulative GPA of 3.127, even while working between 20-40 hours per quarter while employed at Meijun.
\end{itemize}

\section{Notable Projects}
\vspace{0.5em}


\noindent\begin{large}\textsc{Fitness Tracking App:}\end{large} \textit{12/2015 - 6/2017} (iOS, Android, with webapp admin portal)\\
Architected and implemented a fitness based app and admin portal. App interfaces with multiple third-party Bluetooth LE fitness wearables. Occasionally had to reverse engineer low-level SDKs. Reliably backup/restore data to/from the server, successfully taking variable timezones and potentially overlapping data into account.


%Researched and implemented methods for creating music/sound via a NeuroSky Brain Computer Interface (BCI). Combined multiple APIs to create an Android app that produces sounds controlled by various deliberate brain-wave measures.


%\noindent\begin{large}\textsc{Front-end MVC Framework:}\end{large}\\
%Developed a state-based, lightweight framework for a client's single-page web application. Created a custom solution due to client requirements. Applied Object Oriented Design principles to improve development time of the end product. Designed with reusability and security in mind.


\noindent\begin{large}\textsc{Browser Tracking Research Project}\end{large} \textit{4/2017 - Present}\\
Independent research project under supervision of grad-student. Investigate potential browser tracking methods to determine if specific JavaScript functions are being used maliciously. Profile functions in Chrome using  an extension and overloading of low-level APIs. Currently working to create automated execution of tests on large numbers of websites to collect data for analysis.


\section{Skills}
\vspace{0.5em}
\noindent\begin{large}\textsc{Languages:}\end{large}
\([\)fluent\(]\) Java, C++ (6 years), PHP (3 years), HTML5, CSS3, JavaScript, Objective-C (2 years), \([\)familiar\(]\) Swift, Python


\noindent\begin{large}\textsc{Technologies/Frameworks:}\end{large}
jQuery, iOS, Android, Node.js/Sails.js, Bluetooth LE, Postgres, MySQL, Linux, AWS (primarily EC2 and S3), Wordpress (custom themes and plugins)

\noindent\begin{large}\textsc{Miscellaneous:}\end{large} Cyber Security, Networking, Agile, Team Leadership, Effective Time Management

\end{document}